Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-07-04 WRITEUP/ms.tex

We start by considering the distributions of MCC molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
\end{equation}
%
We show in \Fig{dist} the distributions from the combination of the three considered evolution stages. We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc (top panels) and a high cut \footnote{The highest density threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest structure. However, not all evolutionary stages considered have at least one MCC at this highest density threshold, so we consider MCCs identified with the second highest density threshold instead.} of $n_{\rm cut}$\eq18.96\,\cc, (lower panels).
%
Overall, the mass of all MCCs identified ranges from $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, whereas the gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,1.

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_fgas.pdf}
\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$. The most massive structures identified with a low $f_{\rm gas}$ correspond to the molecular disk/arms of \flower (see also \Fig{vv}).
%
Thus, these structures encompass a large amount of stellar mass that is already assembled in \flower. These disk/arm structures are excluded in the discussion of MCC dynamics in the remainder of this paper. 
\label{fig:stellarRatio16}}
\end{figure}

The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is identified as a single component at low $n_{\rm cut}$. This main disk component occupies the top left corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$. The velocity dispersion of such structure is dominated by bulk motions, as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower. The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MCC}).
%
Excluding the structure corresponding to the molecular disk, the velocity dispersions of most MCCs in the accreting phase of \flower are dominated by turbulent motions. On the other hand, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MCCs in the quiescent disk-like phase.
%
For these reasons, the most massive MCCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done so for an observational study.

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation (middle), and $\sigma_{\rm gas}^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for MCCs (star symbols) identified in the two most extreme evolutionary stages of \flower\ --- accreting (left) and starburst (right).
%
Star symbols are color-coded by density thresholds $n_{\rm cut}$, as illustrated by the colorbar shown on the right.
%
Gas-only $\alpha_{\rm vir}$ (orange star symbols) is overplotted, and is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs since they are gas-dominated (see \Fig{stellarRatio16}) \AP{I think the orange points makes the figure more messy, an alternative would to remove them and discuss the point in the text}. 
%
Stability of the biggest structures is strongly influenced by the stellar component, given their low $f_{\rm gas}$ (see \Fig{stellarRatio16} and \Sec{dist}).
%
The gray dotted lines shown in the bottom panels correspond to the various annotated external pressures needed in order for the gas to be in equilibrium, see Equation~\ref{eqn:v0}. Literature data are taken from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, 
Swinbank11a, Leroy15a, Kauffmann17a,Kauffmann17b}. MCCs in the starburst phrase have lower $\alpha_{\rm vir}$ than in the accreting phase.
\label{fig:larsons_single}}
\end{figure*}

@@

During the accreting phase, MCCs in \flower\ are characterized by large velocity dispersions ($\sigma \simeq 100 {\rm km s}^{-1}$) and sizes ($R\simeq 100$\,pc). These values are comparable to those found in starburst galaxies, such as the nearby gas-rich galaxy M64 and the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 \citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.

While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
% 
The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability. On the other hand, the MCCs in this phase are mostly stable, with 
virial parameter comparable to some of the molecular structures observed in the Milky Way but the former is more massive.

>>>>

We start by considering the distributions of MCC molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
\end{equation}
%
We show in \Fig{dist} the distributions
%mm2 considering all the evolutionary stages of \flower and dividing the sample in
%a low  ($n_{\rm cut}$\eq0.32\,\cc, top panels) and a high ($n_{\rm
%cut}$\eq18.96\,\cc, lower panels) density cuts 
      from the combination of the three considered evolution stages.
      We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc
      (top panels) and a high cut \footnote{The highest density
        threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to
        a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the
        densest structure. However, not all evolutionary stages
        considered have at least one MCC at this highest density
        threshold, so we consider MCCs identified with the second
        highest density threshold instead.}.
 of $n_{\rm cut}$\eq18.96\,\cc, (lower panels).
%
Overall, the mass of all MCCs identified ranges from $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun, 
whereas the gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,1.

% address the biggest MCC = molecular disk of \flower
%mm2 [This and following figures would be better with the  color bar
%from Figure 7 rather than the prominent stars at the bottom...]
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{\figpath/cloud-mass_fgas.pdf}
\caption{Cloud mass and stellar-to-gas mass ratio of MCCs identified in the accreting phase of \flower with different $n_{\rm cut}$. The most massive structures identified with a low $f_{\rm gas}$ correspond to the molecular disk/arms of \flower (see also \Fig{vv}).
%
Thus, these structures encompass a large amount of stellar mass that is already assembled in \flower. These disk/arm structures are excluded in the discussion of MCC dynamics in the remainder of this paper. 
\label{fig:stellarRatio16}}
\end{figure}

The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond
to the molecular disk of the galaxy (see e.g., \Fig{MCC}), which is
identified as a single component at low $n_{\rm cut}$. This main disk
component
% mm2 occupy the top right   [left not right!]
          occupies the top left
corner of \Fig{stellarRatio16}, with a low gas mass fraction of
$f_{\rm gas}< 5\%$. The velocity dispersion of such a structure is
dominated by bulk
% mm2 motions,
rotational motion,
as shown in \Fig{vv}, where we compare the velocity dispersions of MCCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower. The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MCC}).
%
Excluding the structure corresponding to the molecular disk, the
velocity dispersions of most MCCs in the accreting phase of \flower
are dominated by turbulent motions, 
% mm2 . On the other hand, [the first hand is missing]
  while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at
  least comparable to $\sigma_{\rm NT}$ for almost half the MCCs.
%mm2 in the quiescent disk-like phase.
%
For these reasons, the most massive MCCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done for an observational study.

@@

\begin{figure*}
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/3by2_clumpProp_ss16-ss22.png}
\caption{
Linewidth-size relation (top), $\alpha_{\rm vir}$-mass relation (middle), and $\sigma_{\rm gas}^2/R$-$\Sigma_{\rm gas}$ relation (bottom) for MCCs (star symbols) identified in the two most extreme evolutionary stages of \flower\ --- accreting (left) and starburst (right).
%
Star symbols are color-coded by density thresholds $n_{\rm cut}$, as illustrated by the colorbar shown on the right.
%
Gas-only $\alpha_{\rm vir}$ (orange star symbols) is overplotted, and is of the same order of magnitude as $\alpha_{\rm vir, tot}$ for most MCCs since they are gas-dominated (see \Fig{stellarRatio16}) \AP{I think the orange points makes the figure more messy, an alternative would to remove them and discuss the point in the text}. 
%
Stability of the biggest structures is strongly influenced by the stellar component, given their low $f_{\rm gas}$ (see \Fig{stellarRatio16} and \Sec{dist}).
%
The gray dotted lines shown in the bottom panels correspond to the various annotated external pressures needed in order for the gas to be in equilibrium, see Equation~\ref{eqn:v0}. Literature data are taken from \citet{Larson81a, Heyer04a, Rosolowsky05a, Bolatto08a, 
Swinbank11a, Leroy15a, Kauffmann17a}, and \citet{Kauffmann17b}. MCCs in the starburst phrase have lower $\alpha_{\rm vir}$ than in the accreting phase.
\label{fig:larsons_single}}
\end{figure*}

@@

During the accreting phase, MCCs in \flower\ are characterized by
large velocity dispersions ($\sigma \simeq 100 \mbox{ km s}^{-1}$) and sizes ($R\simeq 100$\,pc). These values are comparable to those found in starburst galaxies, such as the nearby gas-rich galaxy M64 and the $z$\ssim2 starbursting disk galaxy SMM\,J2135-0102 \citep{Rosolowsky05a, Swinbank11a}, but are higher than those found in the Milky Way and extragalactic GMCs by an order of magnitude \citep{Heyer04a, Bolatto08a}.

While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
% 
The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main 
disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower
explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential 
influences the overall stability. On the other hand, the MCCs in this phase are mostly stable, with 
virial parameter comparable to some of the molecular structures
observed in the Milky Way,
% mm2 but the former is
     though the MCCs are
     more massive.
